Towards a Practical Face Recognition System: \\ Robust Alignment and Illumination by Sparse Representation\\ (Supplementary Materials)

### 2011-04-06 bios/bios.tex
Added Zihan's bio, working on supp. material

\biospace
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{Zihan Zhou}
received... {\bf PLACEHOLDER}
\end{IEEEbiography}

>>>>

\biospace
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/zihan}}]{Zihan Zhou}
Zihan Zhou received the bachelor's degree in automation from Tsinghua
University, China, in 2007. Since then, he has been with University of Illinois
at Urbana-Champaign, where he received the MS degree in electrical and computer
engineering and where he is now working toward the PhD degree. During the
summer of 2009, he was a research intern with Microsoft Research Asia, Beijing.
His research interests include computer vision, signal processing and machine
learning. He is a student member of the IEEE.
\end{IEEEbiography}

### 2011-04-06 supplementary_material.tex
Added Zihan's bio, working on supp. material

%% bare_jrnl.tex
%% V1.1
%% 2002/08/13
%% by Michael Shell
%% mshell@ece.gatech.edu
%%
%% NOTE: This text file uses MS Windows line feed conventions. When (human)
%% reading this file on other platforms, you may have to use a text
%% editor that can handle lines terminated by the MS Windows line feed
%% characters (0x0D 0x0A).
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.6 or later) with an IEEE journal paper.
%%
%% Support sites:
%% http://www.ieee.org
%% and/or
%% http://www.ctan.org/tex-archive/macros/latex/contrib/supported/IEEEtran/
%%
%% This code is offered as-is - no warranty - user assumes all risk.
%% Free to use, distribute and modify.

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% Testflow can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/supported/IEEEtran/testflow

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print. Authors are encouraged to use U.S. letter paper when
% submitting to IEEE. Use the testflow package mentioned above to verify
% correct handling of both paper sizes by the author's LaTeX system.
%
% Also note that the "draftcls", not "draft", option should be used if
% it is desired that the figures are to be displayed in draft mode.

% *************************************************************************
% You can now use this template both for submitting to peer review and,
% if your paper is accepted, for sending in final publication materials.
% To change from peer review format (single column, double-spaced) to
% final publication format (double column, single-spaced), just move the
% comment-line sign (%) from one \documentclass line to the other.
% The first is for peer review format(single column), the second is for final publication(double column).

%\documentclass[12pt,journal,draftcls,letterpaper,onecolumn]{IEEEtran}
%\documentclass[9.5pt,journal,final,compsoc,twocolumn]{IEEEtran}

\documentclass[10pt,journal,letterpaper,compsoc]{IEEEtran} % from the new style file.  supposedly double column.

% *************************************************************************

@@

\begin{document}
%
% paper title
\title{Towards a Practical Face Recognition System: \\ Robust Alignment and
Illumination by Sparse Representation}
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
\author{Andrew~Wagner,~\IEEEmembership{Student~Member,~IEEE,}
        John~Wright,~\IEEEmembership{Member,~IEEE,}
        Arvind~Ganesh,~\IEEEmembership{Student~Member,~IEEE,}
        Zihan~Zhou,~\IEEEmembership{Student~Member,~IEEE,}
        Hossein~Mobahi,
        and~Yi~Ma,~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
\thanks{A. Wagner, A. Ganesh, Z. Zhou, and Y. Ma are with the Dept. of Electrical and Computer Engineering at the University of Illinois at Urbana-Champaign. H. Mobahi is with the Computer Science Dept. at the University of Illinois at Urbana-Champaign.  J. Wright and Y. Ma are with Microsoft Research Asia.  Corresponding author: Andrew Wagner, awagner@illinois.edu, 1308 W. Main st. Urbana, IL 61801, (312) 343-1380.}}% <-this % stops a space

@@

% If you want to put a publisher's ID mark on the page
% (can leave text blank if you just want to see how the
% text height on the first page will be reduced by IEEE)
%\pubid{0000--0000/00\$00.00~\copyright~2002 IEEE}

% use only for invited papers
%\specialpapernotice{(Invited Paper)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%% ABSTRACT
\IEEEcompsoctitleabstractindextext{
\vspace{0mm}
\begin{abstract}
Many classic and contemporary face recognition algorithms work
well on public data sets, but degrade sharply when they are
used in a real recognition system. This is mostly due to the
difficulty of simultaneously handling variations in
illumination, image misalignment, and occlusion in the test
image. We consider a scenario where the training images are
well controlled, and test images are only loosely controlled.
We propose a conceptually simple face recognition system that
achieves a high degree of robustness and stability to
illumination variation, image misalignment, and partial
occlusion. The system uses tools from sparse representation to
align a test face image to a set of frontal training images.
The region of attraction of our alignment algorithm is computed
empirically for public face datasets such as Multi-PIE. We
demonstrate how to capture a set of training images with enough
illumination variation that they span test images taken under
uncontrolled illumination. In order to evaluate how our
algorithms work under practical testing conditions, we have
implemented a complete face recognition system, including a
projector-based training acquisition system. Our system can
efficiently and effectively recognize faces under a variety of
realistic conditions, using only frontal images under the
proposed illuminations as training.\vspace{0mm}
\end{abstract}

>>>>

\documentclass[10pt,journal,letterpaper,compsoc]{IEEEtran}

@@

\begin{document}
%
% paper title
\title{Towards a Practical Face Recognition System: \\ Robust Alignment and
Illumination by Sparse Representation\\
(Supplementary Materials)}
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
\author{Andrew~Wagner,~\IEEEmembership{Student~Member,~IEEE,}
        John~Wright,~\IEEEmembership{Member,~IEEE,}
        Arvind~Ganesh,~\IEEEmembership{Student~Member,~IEEE,}
        Zihan~Zhou,~\IEEEmembership{Student~Member,~IEEE,}
        Hossein~Mobahi,
        and~Yi~Ma,~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
\thanks{A. Wagner, A. Ganesh, Z. Zhou, and Y. Ma are with the Dept. of Electrical and Computer Engineering at the University of Illinois at Urbana-Champaign. H. Mobahi is with the Computer Science Dept. at the University of Illinois at Urbana-Champaign.  J. Wright and Y. Ma are with Microsoft Research Asia.  Corresponding author: Andrew Wagner, awagner@illinois.edu, 1308 W. Main st. Urbana, IL 61801, (312) 343-1380.}}% <-this % stops a space

@@
